Lemma 1

### 2021-03-29 notes/jessie-russian-lemma.tex
Adding notes from last meeting

>>>>

\section{More direct proof}
Consider the sets
\begin{align*}
A &:= \partial \E_p L(u,Y)\\
B &:= \{\E_p V(Y) \mid V\textrm{ measurable, } V(y) \in \partial L(u,y) \, p-a.s.\}\\
Z &:= \{\E_p V(Y) \mid V\textrm{ measurable, } V(y) \in \partial L(u,y) \, \forall y \in \Y \} 
\end{align*}

We want to show $A = Z$; the Russian paper shows $A =B$.
First, we have $A \supseteq B$ by definition of subdifferential, and $B \supseteq Z$ trivially, so $A \supseteq Z$.
It is left to show $A \subseteq Z$.

As $A$ is a subdifferential of a finite, convex loss defined on $\reals^d$, we have $A$ convex and compact.

In particular, if \jessie{CONDITION} in $A$ are described by elements of $Z$, then anything in $A$ can be described by an element of $Z$ by its convexity and closedness.

Hypothesis: \jessie{CONDITION} = exposed faces in the relative boundary of $A$.
